Abstract

### 2025-10-22 output/Main_text.Rmd
Reformulate orthogonalty in Reckase's (1985) Eq. 3
It states clearly that orthogonality is assumed "as early as Eq. 3"
Correct reference to equations
After including new equations 22 and 23, these ones cannot be considered contiguous.

As Equation \@ref(eq:M2PL-formula-polar) shows, the inner product matrix is
involved in the expression of the model in polar coordinates.
Importantly, this shows that
Reckase's [-@reckase_difficulty_1985] Equation 3 (p. 403)
assumes the orthonormality of the latent space, as we stated before.

@@

The item location $`r MIL_PARAM`$ is defined as the distance and direction
from the origin to the point of maximum slope [@reckase_difficulty_1985].
By analogy with the unidimensional case, $`r MDISC_SYM`$ is defined as
$4 `r SLOPE_MAX_PARAM`$ [@reckase_discriminating_1991].
Hence we may define the $`r MIL_PARAM`$ and $`r MDISC_SYM`$ using
Equations \@ref(eq:distance-param) through \@ref(eq:dir-cos-vec-test-space).
However, as they depend on the inner product matrix $`r INNER_PROD_MATRIX`$,
the choice we make of this matrix will lead us to different definitions of
the parameters.

>>>>

As Equation \@ref(eq:M2PL-formula-polar) shows, the inner product matrix is
involved in the expression of the model in polar coordinates.
Importantly, this shows that the orthogonality of the latent space in
@reckase_difficulty_1985 is assumed as early on as in Equation 3 (p. 403),
as we stated before.

@@

The item location $`r MIL_PARAM`$ is defined as the distance and direction
from the origin to the point of maximum slope [@reckase_difficulty_1985].
By analogy with the unidimensional case, $`r MDISC_SYM`$ is defined as
$4 `r SLOPE_MAX_PARAM`$ [@reckase_discriminating_1991].
Hence we may define the $`r MIL_PARAM`$ and $`r MDISC_SYM`$ using
Equations \@ref(eq:distance-param), \@ref(eq:slope-param),
and \@ref(eq:dir-cos-vec-test-space).
However, as they depend on the inner product matrix $`r INNER_PROD_MATRIX`$,
the choice we make of this matrix will lead us to different definitions of
the parameters.
